Verifying Demonstrations

### 2017-10-04 protocol.tex
Changes arrow tips in proof-share overview
Completes proof-share diagram

\begin{frame}
\begin{figure}
  \centering
  \begin{tikzpicture}
    \tikzset{grow'=left,level distance=5em}
    \Tree [.proof
    {share}
    [.{share} {\(wid\)} {\(l\)} {$t_s$} [.{\(pid\)} [.{\(cid\)} manifesto ] ]
    %[.tsig {$t_s''$} ]
    ]
    {share}
    ]
  \end{tikzpicture}
  \mode<article>{%
  \caption{%
    The proof depends on several proof shares.
    Each share depends on the protester's identifier (\(pid\), which depends on 
    the cause identifier, \(cid\)),
    the head of the blockchain (\(t_s\)), the location (\(l\)) and the witness 
    identifier (\(wid\)).
  }}%
  \label{fig:ProofFig}
\end{figure}
\end{frame}

>>>>

\begin{frame}
\begin{figure}
  \centering
  \begin{tikzpicture}[%
    -Latex,
    item/.style={rectangle,draw},
    edge from parent/.style={}
    ]
    \tikzset{%
      %grow'=left,%
      %level distance=5em%
    }
    \node[item] (proof) {Proof share}
      child {%
        node[item] (pid) {$pid$}
        child {%
          node[item] (cid) {$cid$}
          child {%
            node[item] (manifesto) {Manifesto}
          }
        }
      }
      child {%
        node[item] (wid) {$wid$}
      }
      child {%
        node[item] (ts) {$t_s$}
      }
      child {%
        node[item] (l) {$l$}
      }
      child {%
        node[item] (wsig) {$wsig$}
      }
      ;

      \path[every node/.style={font=\small}]
      (pid) edge node [anchor=east] {$\in$} (proof)
      (ts) edge node [anchor=east] {$\in$} (proof)
      (l) edge node [anchor=east] {$\in$} (proof)
      (wid) edge node [anchor=east] {$\in$} (proof)
      (wsig) edge node [anchor=east] {$\in$} (proof)
      ;

      \path[every node/.style={font=\small}]
      (manifesto) edge node [anchor=east] {$H(\cdot)$} (cid)
      (cid) edge node [anchor=east] {$PRF_{k_p}(\cdot)$} (pid)
      (pid) edge[bend right] node [anchor=north west] {$PRF_{k_w}(\cdot)$} (wid)
      % wsig
      (l) edge[bend right] (wsig)
      (ts) edge[bend right] (wsig)
      (wid) edge[bend right] node [anchor=north west] {$PRF_{k_w}(\cdot, \cdot, 
        \cdot)$} (wsig)
      ;

  \end{tikzpicture}
  \mode<article>{%
  \caption{%
    Structure of a proof share.
    The protester's identifier \(pid\) is computed using the protester's key 
    \(k_p\).
    The witness's identifier \(wid\) is computed using the witness's key 
    \(k_w\).
    \(t_s\) is a time interval and \(l\) is the coordinates of an area.
  }}%
  \label{fig:ProofFig}
\end{figure}
\end{frame}
